\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-03-01 paper.tex
Reworked (simplified, really) reference to DyKnow

\uwds provides an exemplary client ({\tt spatial\_relations}) to compute both
allo-centric (independent of the viewpoint like {\tt isIn} or {\tt isOn}) and
ego-centric (\ie viewer-dependent, like {\tt inFrontOf} or {\tt leftOf}) spatial relations
between objects.
%(Figure~\ref{fig|spatialrelations}).
Other libraries, like QSRLib~\cite{gatsoulis2016qsrlib}, that implement
computational models of Qualitative Spatial Relations could be trivially
combined with \uwds to provide more advanced geometric analysis.

@@

Like traditional robotic middleware, \uwds offers a form of distributed
computation based on message passing. However, it distinguishes itself from
existing middleware in significant ways. Most importantly, \uwds purposefully
does not offer any \emph{general} capability to distribute computation and data
flow amongst independent components: it focusses specifically on distributing
environment models, both spatial (geometric models) and temporal (events and
situations). In that sense, \uwds really is a \emph{distributed datastructure}
that addresses the specific needs of spatio-temporal modelling,
including the modelling of hypothetical, alternative world models, something
that traditional middlewares like ROS do not address adequately.

@@

>>>>

\uwds provides an exemplary client ({\tt spatial\_relations}) to compute both
allo-centric (independent of the viewpoint like {\tt isIn} or {\tt isOn}) and
ego-centric (\ie viewer-dependent, like {\tt inFrontOf} or {\tt leftOf}) spatial relations
between objects.
%(Figure~\ref{fig|spatialrelations}).
Other libraries, like QSRLib~\cite{gatsoulis2016qsrlib}, that implement
computational models of Qualitative Spatial Relations, could be trivially
combined with \uwds to provide more advanced geometric analysis.
Future developments will also include the results of the more basic
research on spatio-temporal reasoning for robotics, led by de Leng and
Heintz~\cite{deleng2016qualitative}.

@@

Like traditional robotic middleware, \uwds offers a form of distributed
computation based on message passing. However, it distinguishes itself from
existing middlewares (including ROS extensions like
DyKnow~\cite{de_leng_dyknow:_2016}) in significant ways. Most importantly,
\uwds purposefully does not offer any \emph{general} capability to distribute
computation and data streams amongst independent components: it focusses
specifically on distributing environment models, both spatial (geometric
models) and temporal (events and situations). In that sense, \uwds really is a
\emph{distributed datastructure} that addresses the specific needs of
spatio-temporal modelling, including the modelling of hypothetical, alternative
world models, something that traditional middlewares like ROS do not address
adequately. Second, and as presented above, \uwds offers specific mechanisms
for the representation and manipulation of alternative world models that are
not directly achievable with traditional tools.

@@

%\uwds also differs from the DyKnow framework~\cite{de_leng_dyknow:_2016}.
%DyKnow investigates stream reasoning as a central concept for spatial and
%temporal modelling, with a recent focus on semantic-aware auto-configurable
%systems~\cite{leng_towards_2017}. \uwds
%only distribute one type of spatial (scene graph) and temporal (timeline)
%datastructures, as explained above.
